Influence of School Closure on COVID-19 Contaminations in Ireland and Repercussions across Age Groups

### 2022-01-18 manuscript/manuscript.Rmd
upgrade

```{r setup, include = FALSE}
# libraries --------------------------------------------------------------------
library(here)
library(janitor)
library(knitr)
library(mgcv)
library(patchwork)
library(RTransferEntropy)
library(tidyverse)
library(zoo)

@@

# df_school |> 
#   filter(schools_closed == 1) |> 
#   count(schools_closure_wave) |> 
#   rename(schools_closure_wave_n = n)

@@

# df_school_long |> 
#   filter(schools_closure_day == 1 & age_group == "aged1to4") |> 
#   select(date, schools_closure_wave, schools_closure_wave_n)

# analyses ---------------------------------------------------------------------
gam_model <- 
  gam(
    covid_cases_7davg ~ age_group +
      s(schools_time_since_closure, by = age_group) +
      s(schools_time_since_closure, schools_closure_wave, bs = "fs"),
    data = df_school_long,
    method = "REML",
    family = nb()
  )

# analyses ---------------------------------------------------------------------
source(here("analysis/gam_analysis.R"))
source(here("analysis/te_analysis.R"))

```

@@

```{r gam, fig.width=4.5, fig.height=3, fig.cap="(ref:gam)"}
gam_plot_1 + gam_plot_2 + gam_plot_3
```

>>>>

```{r setup, include = FALSE}
# libraries --------------------------------------------------------------------
library(gratia)
library(here)
library(janitor)
library(knitr)
library(mgcv)
library(RTransferEntropy)
library(tidyverse)
library(zoo)

@@

df_school |>
  filter(schools_closed == 1) |>
  count(schools_closure_wave) |>
  rename(schools_closure_wave_n = n)

@@

df_school_long |>
  filter(schools_closure_day == 1 & age_group == "aged1to4") |>
  select(date, schools_closure_wave, schools_closure_wave_n)
```

```{r analyses, cache=TRUE}
source(here("analysis/gam_analysis.R"))
source(here("analysis/te_analysis.R"))
```

@@

```{r gam, fig.width=4.5, fig.height=3, fig.cap="(ref:gam)"}
gam_plot
```
